Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-16 src/tex/ms.tex
statement about GW190720 seglen

We carry out \ac{PE} using a custom version of \textsc{Bilby} \citep{Bilby}, that applies Eq.~\eqref{eq:waveform_modification} for any \ac{GR} baseline waveform.
We depart from the \ac{PE} configuration as in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, with \textsc{IMRPhenomXPHM} as the reference waveform.
We apply a distance prior which is uniform in comoving volume and source frame time instead of a power law distribution used in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, and set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$.

For GW190521, we increase the maximum distance of the distance prior to $1.5$ times the original value, as the birefringence effect enables the probability of a larger distance.

>>>>

We carry out \ac{PE} using a custom version of \textsc{Bilby} \citep{Bilby}, that applies Eq.~\eqref{eq:waveform_modification} for any \ac{GR} baseline waveform.
We take the \ac{PE} configuration as in \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} as a starting point, with \textsc{IMRPhenomXPHM} \citep{Pratten:2020ceb} as the reference waveform.
We apply a distance prior which is uniform in comoving volume and source frame time instead of a power law distribution used in \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, and set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$.

For GW190521, we increase the maximum distance of the distance prior to $1.5\times$ the original value, as the birefringence effect enables the probability of a larger distance.
For GW190720, we decrease the analysis segment to 8 s from 16 s, in order to accomodate missing data near the edges of the 16 s segment in Virgo.
